\morus: Biases in the Stream

### 2018-05-10 morusAC_06_Discussion.tex
Less apologetic

However, \cipher{MORUS1280} with a 256-bit key claims a security level
of 256 bits for confidentiality, and an attack with complexity $2^{152}$
should violate this claim, even if it is not practical.

>>>>

However, \cipher{MORUS1280} with a 256-bit key claims a security level
of 256 bits for confidentiality, and an attack with complexity $2^{152}$
violates this claim, even if it is not practical.
